---
title: "Coronavirus"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    vertical_layout: fill
---


```{r setup, include=FALSE}

library(readr)
library(dplyr)
library(tidyr)
library(lubridate)
library(plotly)
## get confirmed cases

confirmed <- read_csv(file = "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Confirmed.csv")

## get death cases

death <- read_csv(file = "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Deaths.csv")

## get recovered cases

recovered <- read_csv(file = "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_19-covid-Recovered.csv")

## country data

#country_data <- read_csv(file = 'data/country_profile_variables.csv')


## temperatures

temperature_max <- read_csv('https://raw.githubusercontent.com/imantsm/COVID-19/master/csv/tMax.csv')

temperature_min <- read_csv('https://raw.githubusercontent.com/imantsm/COVID-19/master/csv/tMin.csv')          

##### data treatment

library(sp)
library(rworldmap)

# The single argument to this function, points, is a data.frame in which:
#   - column 1 contains the longitude in degrees
#   - column 2 contains the latitude in degrees
coords2continent = function(points)
{  
  countriesSP <- getMap(resolution='low')
  #countriesSP <- getMap(resolution='high') #you could use high res map from rworldxtra if you were concerned about detail
  
  # converting points to a SpatialPoints object
  # setting CRS directly to that from rworldmap
  pointsSP = SpatialPoints(points, proj4string=CRS(proj4string(countriesSP)))  
  
  
  # use 'over' to get indices of the Polygons object containing each point 
  indices = over(pointsSP, countriesSP)
  
  #indices$continent   # returns the continent (6 continent model)
  indices$REGION   # returns the continent (7 continent model)
  #indices$ADMIN  #returns country name
  #indices$ISO3 # returns the ISO3 code 
}






confirmed <- confirmed %>% 
  ## convert the dataset from wide to long
  pivot_longer(., cols = 5:ncol(confirmed), names_to = "Date", values_to = "Confirmed") %>% 
  ## correct portugal values
  mutate(
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/2/20"),2,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/3/20"),4,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/4/20"),6,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/5/20"),9,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/6/20"),13,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/7/20"),21,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/8/20"),30,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/9/20"),39,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/10/20"),41,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/11/20"),59,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/12/20"),78,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/13/20"),112,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/14/20"),169,Confirmed),
    Confirmed = if_else((`Country/Region`=="Portugal") & (Date == "3/18/20"),642,Confirmed),
    Confirmed = if_else((`Country/Region`=="Italy") & (Date == "3/12/20"),15113,Confirmed),
    Confirmed = if_else((`Country/Region`=="Spain") & (Date == "3/12/20"),3146,Confirmed),
    Confirmed = if_else((`Country/Region`=="France") & (`Province/State`=="France") & (Date == "3/12/20"),2876,Confirmed),
    Confirmed = if_else((`Country/Region`=="France") & (`Province/State`=="France") & (Date == "3/15/20"),5423,Confirmed),
    Confirmed = if_else((`Country/Region`=="United Kingdom") & (`Province/State`=="United Kingdom") & (Date == "3/12/20"),590,Confirmed),
    Confirmed = if_else((`Country/Region`=="Germany") & (Date == "3/12/20"),2745,Confirmed)
  ) %>% 
  ## Convert the date column to a date format
  mutate(Date = mdy(Date)) %>% 
  rename(
    State = `Province/State`,
    Country = `Country/Region`
  ) %>% 
  group_by(Country, State) %>% 
  arrange(Date) %>% 
  mutate(
    Confirmed_day = Confirmed - lag(Confirmed, default = 0),
    Continent = coords2continent(data.frame(lon=c(Long), lat=c(Lat)))) %>% 
  ungroup() %>% 
  mutate_if(is.factor, as.character) %>% 
  mutate(
    Continent = if_else(Country=="Australia","Australia",Continent),
    Continent = if_else(Country=="Canada","North America",Continent),
    Continent = if_else(Country=="China","Asia",Continent),
    Continent = if_else(Country=="Denmark","Europe",Continent),
    Continent = if_else(Country=="France","Europe",Continent),
    Continent = if_else(Country=="Netherlands","Europe",Continent),
    Continent = if_else(Country=="United Kingdom","Europe",Continent),
    Continent = if_else(Country=="US","North America",Continent),
    Continent = if_else(Country=="Monaco","Europe",Continent),
    Continent = if_else(Country=="Philippines","Asia",Continent),
    Continent = if_else(Country=="New Zealand","Europe",Continent),
    Continent = if_else(Country=="Saint Vincent and the Grenadine","North America",Continent)
         ) %>%
  select(Continent, State, Country, Lat, Long, Date, Confirmed, Confirmed_day) %>% 
  arrange(State, Continent, Country, Date) %>%
  data.frame()


death <- death %>% 
  ## convert the dataset from wide to long
  pivot_longer(., cols = 5:ncol(death), names_to = "Date", values_to = "Death") %>% 
  ## Convert the date column to a date format
  mutate(Date = mdy(Date)) %>% 
  rename(
    State = `Province/State`,
    Country = `Country/Region`
  ) %>% 
  group_by(Country, State) %>% 
  arrange(Date) %>% 
  mutate(Death_day = Death - lag(Death, default = 0),
         Continent = coords2continent(data.frame(lon=c(Long), lat=c(Lat)))) %>%
  ungroup() %>% 
  mutate_if(is.factor, as.character) %>% 
  mutate(
    Continent = if_else(Country=="Australia","Australia",Continent),
    Continent = if_else(Country=="Canada","North America",Continent),
    Continent = if_else(Country=="China","Asia",Continent),
    Continent = if_else(Country=="Denmark","Europe",Continent),
    Continent = if_else(Country=="France","Europe",Continent),
    Continent = if_else(Country=="Netherlands","Europe",Continent),
    Continent = if_else(Country=="United Kingdom","Europe",Continent),
    Continent = if_else(Country=="US","North America",Continent),
    Continent = if_else(Country=="Monaco","Europe",Continent),
    Continent = if_else(Country=="Philippines","Asia",Continent),
    Continent = if_else(Country=="New Zealand","Europe",Continent),
    Continent = if_else(Country=="Saint Vincent and the Grenadine","North America",Continent)
  ) %>%
  select(Continent, State, Country, Lat, Long, Date, Death, Death_day) %>% 
  arrange(State, Continent, Country, Date) %>% 
  ungroup() %>% 
  data.frame()

recovered <- recovered %>% 
  ## convert the dataset from wide to long
  pivot_longer(., cols = 5:ncol(recovered), names_to = "Date", values_to = "Recovered") %>% 
  ## Convert the date column to a date format
  mutate(Date = mdy(Date)) %>% 
  rename(
    State = `Province/State`,
    Country = `Country/Region`
  ) %>% 
  group_by(Country, State) %>% 
  arrange(Date) %>% 
  mutate(Recovered_day = Recovered - lag(Recovered, default = 0),
         Continent = coords2continent(data.frame(lon=c(Long), lat=c(Lat)))) %>%
  ungroup() %>% 
  mutate_if(is.factor, as.character) %>% 
  mutate(
    Continent = if_else(Country=="Australia","Australia",Continent),
    Continent = if_else(Country=="Canada","North America",Continent),
    Continent = if_else(Country=="China","Asia",Continent),
    Continent = if_else(Country=="Denmark","Europe",Continent),
    Continent = if_else(Country=="France","Europe",Continent),
    Continent = if_else(Country=="Netherlands","Europe",Continent),
    Continent = if_else(Country=="United Kingdom","Europe",Continent),
    Continent = if_else(Country=="US","North America",Continent),
    Continent = if_else(Country=="Monaco","Europe",Continent),
    Continent = if_else(Country=="Philippines","Asia",Continent),
    Continent = if_else(Country=="New Zealand","Europe",Continent),
    Continent = if_else(Country=="Saint Vincent and the Grenadine","North America",Continent)
  ) %>%
  select(Continent, State, Country, Lat, Long, Date, Recovered, Recovered_day) %>% 
  arrange(State, Country, Date) %>% 
  ungroup() %>% 
  data.frame()

active <- confirmed %>% 
  select(-Confirmed_day) %>% 
  left_join(death[, c("Country","Date","Lat","Long","Death")], 
            by=c("Country"="Country","Date"="Date","Lat"="Lat","Long"="Long")) %>% 
  left_join(recovered[, c("Country","Date","Lat","Long","Recovered")], 
            by=c("Country"="Country","Date"="Date","Lat"="Lat","Long"="Long")) %>% 
  mutate(
    Active = Confirmed - (Death + Recovered)
  ) %>% 
  group_by(Country, State) %>% 
  arrange(Date) %>% 
  mutate(Active_day = Active - lag(Active, default = 0)) %>% 
  select(Continent, State, Country, Lat, Long, Date, Active, Active_day) %>% 
  arrange(State, Country, Date) %>% 
  ungroup() %>% 
  data.frame()

# country_data <- country_data %>% 
#   rename(Country = country,
#          Population = `Population in thousands (2017)`) %>% 
#   mutate(Country = if_else(Country=="Iran (Islamic Republic of)","Iran",Country),
#          Country = if_else(Country=="Republic of Korea","Korea, South",Country),
#          Country = if_else(Country=="United States of America","US",Country),
#          Country = if_else(Country=="Viet Nam","Vietnam",Country),
#          Country = if_else(Country=="Russian Federation","Russia",Country),
#          Country = if_else(Country=="Brunei Darussalam","Brunei",Country),
#          Country = if_else(Country=="The former Yugoslav Republic of Macedonia","North Macedonia",Country),
#          Country = if_else(Country=="Republic of Moldova","Moldova",Country),
#          Country = if_else(Country=="Bolivia (Plurinational State of)","Bolivia",Country),
#          Country = if_else(Country=="Democratic Republic of the Congo","Congo (Kinshasa)",Country),
#          Population = Population*1000)

temperature_max <- temperature_max %>% 
  ## convert the dataset from wide to long
  pivot_longer(., cols = 5:ncol(temperature_max), names_to = "Date", values_to = "TempMax") %>% 
  ## Convert the date column to a date format
  mutate(Date = mdy(Date),
         Continent = coords2continent(data.frame(lon=c(Long), lat=c(Lat)))) %>% 
  rename(
    State = `Province/State`,
    Country = `Country/Region`
  ) %>% 
  ungroup() %>% 
  mutate_if(is.factor, as.character) %>% 
  mutate(
    Continent = if_else(Country=="Australia","Australia",Continent),
    Continent = if_else(Country=="Canada","North America",Continent),
    Continent = if_else(Country=="China","Asia",Continent),
    Continent = if_else(Country=="Denmark","Europe",Continent),
    Continent = if_else(Country=="France","Europe",Continent),
    Continent = if_else(Country=="Netherlands","Europe",Continent),
    Continent = if_else(Country=="United Kingdom","Europe",Continent),
    Continent = if_else(Country=="US","North America",Continent),
    Continent = if_else(Country=="Monaco","Europe",Continent),
    Continent = if_else(Country=="Philippines","Asia",Continent),
    Continent = if_else(Country=="New Zealand","Europe",Continent),
    Continent = if_else(Country=="Saint Vincent and the Grenadine","North America",Continent)
  ) %>%
  select(Continent, State, Country, Lat, Long, Date, TempMax) %>% 
  arrange(Continent, State, Country, Date) %>% 
  data.frame()

temperature_min <- temperature_min %>% 
  ## convert the dataset from wide to long
  pivot_longer(., cols = 5:ncol(temperature_min), names_to = "Date", values_to = "TempMin") %>% 
  ## Convert the date column to a date format
  mutate(Date = mdy(Date),
         Continent = coords2continent(data.frame(lon=c(Long), lat=c(Lat)))) %>% 
  rename(
    State = `Province/State`,
    Country = `Country/Region`
  ) %>% 
  ungroup() %>% 
  mutate_if(is.factor, as.character) %>% 
  mutate(
    Continent = if_else(Country=="Australia","Australia",Continent),
    Continent = if_else(Country=="Canada","North America",Continent),
    Continent = if_else(Country=="China","Asia",Continent),
    Continent = if_else(Country=="Denmark","Europe",Continent),
    Continent = if_else(Country=="France","Europe",Continent),
    Continent = if_else(Country=="Netherlands","Europe",Continent),
    Continent = if_else(Country=="United Kingdom","Europe",Continent),
    Continent = if_else(Country=="US","North America",Continent),
    Continent = if_else(Country=="Monaco","Europe",Continent),
    Continent = if_else(Country=="Philippines","Asia",Continent),
    Continent = if_else(Country=="New Zealand","Europe",Continent),
    Continent = if_else(Country=="Saint Vincent and the Grenadine","North America",Continent)
  ) %>%
  select(Continent, State, Country, Lat, Long, Date, TempMin) %>% 
  arrange(Continent, State, Country, Date) %>% 
  data.frame()

#------------------ Packages ------------------
library(flexdashboard)


`%>%` <- magrittr::`%>%`
#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"
#------------------ Data ------------------
dataset_evo <- active %>% 
        left_join(confirmed %>% 
                select(-c(Continent, State)), by=c("Date"="Date", "Country"="Country", "Lat"="Lat","Long"="Long")) %>% 
    left_join(recovered %>% 
                select(-c(Continent, State)), by=c("Date"="Date", "Country"="Country", "Lat"="Lat","Long"="Long")) %>% 
    left_join(death %>% 
                select(-c(Continent, State)), by=c("Date"="Date", "Country"="Country", "Lat"="Lat","Long"="Long")) %>% 
    select(-c(Confirmed_day, Active_day, Recovered_day, Death_day)) %>% 
    group_by(Continent, Country, Date) %>% 
    summarise(Confirmed = sum(Confirmed), Active = sum(Active), Recovered = sum(Recovered), Death = sum(Death))

dataset_evo_daily <- dataset_evo %>% 
  group_by(Country) %>% 
  arrange(Date) %>% 
  mutate(conf_day = Confirmed - lag(Confirmed, default = 0),
         death_day = Death - lag(Death, default = 0),
         active_day = Active - lag(Active, default = 0),
         recovered_day = Recovered - lag(Recovered, default = 0))

status <- dataset_evo %>% 
  filter(Date == max(Date)) %>% 
  arrange(desc(Confirmed))

# df_daily <- coronavirus %>% 
#   dplyr::group_by(date, type) %>%
#   dplyr::summarise(total = sum(cases, na.rm = TRUE)) %>%
#   tidyr::pivot_wider(names_from = type,
#                      values_from = total) %>%
#   dplyr::arrange(date) %>%
#   dplyr::ungroup() %>%
#   dplyr::mutate(active =  confirmed - death - recovered) %>%
#   dplyr::mutate(confirmed_cum = cumsum(confirmed),
#                 death_cum = cumsum(death),
#                 recovered_cum = cumsum(recovered),
#                 active_cum = cumsum(active))
# 
# 
# df1 <- coronavirus %>% dplyr::filter(date == max(date))

```

Summary
=======================================================================
Row
-----------------------------------------------------------------------

### confirmed {.value-box}

```{r}

valueBox(value = paste(format(sum(status$Confirmed), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed Cases", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```


### active {.value-box}

```{r}
valueBox(value = paste(format(sum(status$Active, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(status$Active, na.rm = TRUE) / sum(status$Confirmed), 1), 
                       "%)", sep = ""), 
         caption = "Active Cases", icon = "fas fa-ambulance", 
         color = active_color)
```

### recovered {.value-box}

```{r}
valueBox(value = paste(format(sum(status$Recovered, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(status$Recovered, na.rm = TRUE) / sum(status$Confirmed), 1), 
                       "%)", sep = ""), 
         caption = "Recovered Cases", icon = "fas fa-heartbeat", 
         color = recovered_color)
```

### death {.value-box}

```{r}

valueBox(value = paste(format(sum(status$Death, na.rm = TRUE), big.mark = ","), " (",
                       round(100 * sum(status$Death, na.rm = TRUE) / sum(status$Confirmed), 1), 
                       "%)", sep = ""),
         caption = "Death Cases", 
         icon = "fas fa-heart-broken", 
         color = death_color)
```


Row
-----------------------------------------------------------------------

### Cases Distribution by Type (Top 25 Countries)

```{r daily_summary}


plotly::plot_ly(data = status[1:30,], 
                x = ~ Country, 
                y = ~ Active, 
                # text =  ~ confirmed, 
                # textposition = 'auto',
                type = "bar", 
                name = "Active",
                marker = list(color = active_color)) %>%
  plotly::add_trace(y = ~ Recovered, 
                    # text =  ~ recovered, 
                    # textposition = 'auto',
                    name = "Recovered",
                    marker = list(color = recovered_color)) %>%
  plotly::add_trace(y = ~ Death, 
                    # text =  ~ death, 
                    # textposition = 'auto',
                    name = "Death",
                    marker = list(color = death_color)) %>%
  plotly::layout(barmode = 'stack',
                 yaxis = list(title = "Total Cases (log scaled)",
                              type = "log"),
                 xaxis = list(title = ""),
                 hovermode = "compare",
                  margin =  list(
                   # l = 60,
                   # r = 40,
                   b = 10,
                   t = 10,
                   pad = 2
                 ))

```

Row {data-width=400}
-----------------------------------------------------------------------


### Daily Cumulative Cases by Type
    
```{r}

# plotly::plot_ly(df_daily, x = ~date, y = ~active_cum, name = 'Active', type = 'scatter', mode = 'none', stackgroup = 'one', fillcolor = "#1f77b4") %>%
# plotly::add_trace(y = ~recovered_cum, name = 'Recovered', fillcolor = "green") %>%
# plotly::add_trace(y = ~death_cum, name = "Death", fillcolor = "red") %>%
#   plotly::layout(title = "",
#          xaxis = list(title = "",
#                       showgrid = FALSE),
#          yaxis = list(title = "Cumulative Number of Cases",
#                       showgrid = FALSE),
#          legend = list(x = 0.1, y = 0.9),
#                  hovermode = "compare")
                 

dataset_evo_daily %>% 
  group_by(Date) %>% 
  summarise(active = sum(active_day), recovered = sum(recovered_day), death = sum(recovered_day)) %>%
  plotly::plot_ly() %>%
  plotly::add_trace(x = ~ Date,
                    y = ~ active,
                    type = "scatter",
                    mode = "lines+markers",
                    name = "Active",
                    line = list(color = active_color),
                    marker = list(color = active_color)) %>%
  plotly::add_trace(x = ~ Date,
                    y = ~ recovered,
                    type = "scatter",
                    mode = "lines+markers",
                    name = "Recovered",
                    line = list(color = recovered_color),
                    marker = list(color = recovered_color)) %>%
  plotly::add_trace(x = ~ Date,
                    y = ~ death,
                    type = "scatter",
                    mode = 'lines+markers',
                    name = "Death",
                    line = list(color = death_color),
                    marker = list(color = death_color)) %>%
   # plotly::add_annotations(x = as.Date("2020-03-01"),
   #                        y = 42716,
   #                        text = paste("# of recovered cases surpass", 
   #                                     "<br>", 
   #                                     "the # of active cases"),
   #                        xref = "x",
   #                        yref = "y",
   #                        arrowhead = 5,
   #                        arrowhead = 3,
   #                        arrowsize = 1,
   #                        showarrow = TRUE,
   #                        ax = -10,
   #                        ay = 90) %>%
  plotly::layout(title = "",
                 yaxis = list(title = "Cumulative Number of Cases"),
                 xaxis = list(title = "Date"),
                 legend = list(x = 0.1, y = 0.9),
                 hovermode = "compare")
  

```


### Recovery and Death Rates by Country
    
```{r}

summary <- dataset_evo %>% 
  filter(Date == max(Date)) %>%
  mutate(recover_rate = Recovered/Confirmed,
         death_rate = Death/Confirmed)  
summary %>%
  DT::datatable(rownames = FALSE,
            colnames = c("Country", "Confirmed", "Recovered", "Death", "Recovery Rate", "Death Rate"),
            options = list(pageLength = nrow(summary), dom = 'tip')) %>%
  DT::formatPercentage("recover_rate", 2) %>%
  DT::formatPercentage("death_rate", 2) 
```


<!-- Trends -->
<!-- ======================================================================= -->


<!-- Column {data-width=400} -->
<!-- ------------------------------------- -->

<!-- ### New Cases - Top 15 Countries (`r  max(coronavirus$date)`) -->

<!-- ```{r} -->
<!-- max_date <- max(coronavirus$date) -->
<!-- coronavirus %>%  -->
<!--   dplyr::filter(type == "confirmed", date == max_date) %>% -->
<!--   dplyr::group_by(Country.Region) %>% -->
<!--   dplyr::summarise(total_cases = sum(cases)) %>% -->
<!--   dplyr::arrange(-total_cases) %>% -->
<!--   dplyr::mutate(country = factor(Country.Region, levels = Country.Region)) %>% -->
<!--   dplyr::ungroup() %>% -->
<!--   dplyr::top_n(n = 15, wt = total_cases) %>% -->
<!--   plotly::plot_ly(x = ~ country, -->
<!--                   y = ~ total_cases, -->
<!--                   text = ~ total_cases, -->
<!--                   textposition = 'auto', -->
<!--                   type = "bar") %>% -->
<!--   plotly::layout(yaxis = list(title = "Number of Cases"), -->
<!--                  xaxis = list(title = ""), -->
<!--                  margin =  list( -->
<!--                    l = 10, -->
<!--                    r = 10, -->
<!--                    b = 10, -->
<!--                    t = 10, -->
<!--                    pad = 2 -->
<!--                  )) -->

<!-- ``` -->


<!-- ### Daily New Cases - China vs. Rest of the World -->

<!-- ```{r} -->
<!-- daily_confirmed <- coronavirus %>% -->
<!--   dplyr::filter(type == "confirmed") %>% -->
<!--   dplyr::mutate(country = dplyr::if_else(Country.Region == "China",  -->
<!--                                          "China",  -->
<!--                                          "Rest of the World")) %>% -->
<!--   dplyr::group_by(date, country) %>% -->
<!--   dplyr::summarise(total = sum(cases)) %>%  -->
<!--   dplyr::ungroup() %>% -->
<!--   tidyr::pivot_wider(names_from = country, values_from = total)  -->

<!-- #---------------------------------------- -->
<!-- # Plotting the data -->

<!-- daily_confirmed %>% -->
<!--   plotly::plot_ly() %>%  -->
<!--   plotly::add_trace(x = ~ date,  -->
<!--                     y = ~ China,  -->
<!--                     type = "scatter",  -->
<!--                     mode = "lines+markers", -->
<!--                     name = "China") %>%  -->
<!--   plotly::add_trace(x = ~ date,  -->
<!--                     y = ~ `Rest of the World`,  -->
<!--                     type = "scatter",  -->
<!--                     mode = "lines+markers", -->
<!--                     name = "Rest of the World") %>%  -->
<!--   plotly::add_annotations(x = as.Date("2020-02-13"), -->
<!--                           y = 15133, -->
<!--                           text = paste("One time adjustment -",  -->
<!--                                        "<br>",  -->
<!--                                        "China modified the diagnostic criteria"), -->
<!--                           xref = "x", -->
<!--                           yref = "y", -->
<!--                           arrowhead = 5, -->
<!--                           arrowhead = 3, -->
<!--                           arrowsize = 1, -->
<!--                           showarrow = TRUE, -->
<!--                           ax = 50, -->
<!--                           ay = -40) %>% -->
<!--   plotly::add_annotations(x = as.Date("2020-02-26"), -->
<!--                           y = 577, -->
<!--                           text = paste("New cases outside of China", "<br>", "surpass the ones inside China"), -->
<!--                           xref = "x", -->
<!--                           yref = "y", -->
<!--                           arrowhead = 5, -->
<!--                           arrowhead = 3, -->
<!--                           arrowsize = 1, -->
<!--                           showarrow = TRUE, -->
<!--                           ax = -70, -->
<!--                           ay = -50) %>% -->
<!--   plotly::layout(title = "", -->
<!--                  legend = list(x = 0.1, y = 0.9), -->
<!--                  yaxis = list(title = "Number of New Cases"), -->
<!--                  xaxis = list(title = "Date"), -->
<!--                  # paper_bgcolor = "black", -->
<!--                  # plot_bgcolor = "black", -->
<!--                  # font = list(color = 'white'), -->
<!--                  hovermode = "compare", -->
<!--                  margin =  list( -->
<!--                    # l = 60, -->
<!--                    # r = 40, -->
<!--                    b = 10, -->
<!--                    t = 10, -->
<!--                    pad = 2 -->
<!--                  )) -->

<!-- ``` -->

<!-- Column {data-width=600} -->
<!-- ------------------------------------- -->

<!-- ### Recovery and Death Rates for Countries with at Least 100 Cases -->

<!-- ```{r} -->
<!-- coronavirus::coronavirus %>%  -->
<!--   # dplyr::filter(Country.Region != "Others") %>% -->
<!--   dplyr::group_by(Country.Region, type) %>% -->
<!--   dplyr::summarise(total_cases = sum(cases)) %>% -->
<!--   tidyr::pivot_wider(names_from = type, values_from = total_cases) %>% -->
<!--   dplyr::arrange(- confirmed) %>% -->
<!--   dplyr::filter(confirmed >= 100) %>% -->
<!--   dplyr::mutate(recover_rate = recovered / confirmed, -->
<!--                 death_rate = death / confirmed) %>%  -->
<!--   dplyr::mutate(recover_rate = dplyr::if_else(is.na(recover_rate), 0, recover_rate), -->
<!--                 death_rate = dplyr::if_else(is.na(death_rate), 0, death_rate)) %>% -->
<!--   dplyr::ungroup() %>% -->
<!--   dplyr::mutate(confirmed_normal = as.numeric(confirmed) / max(as.numeric(confirmed))) %>% -->
<!--   plotly::plot_ly(y = ~ round(100 * recover_rate, 1), -->
<!--                   x = ~ round(100 * death_rate, 1), -->
<!--                   size = ~  log(confirmed), -->
<!--                   sizes = c(5, 70), -->
<!--                   type = 'scatter', mode = 'markers', -->
<!--                   color = ~ Country.Region, -->
<!--                   marker = list(sizemode = 'diameter' , opacity = 0.5), -->
<!--                   hoverinfo = 'text', -->
<!--                   text = ~paste("</br>", Country.Region,  -->
<!--                                 "</br> Confirmed Cases: ", confirmed, -->
<!--                                 "</br> Recovery Rate: ", paste(round(100 * recover_rate, 1), "%", sep = ""), -->
<!--                                 "</br> Death Rate: ",  paste(round(100 * death_rate, 1), "%", sep = "")) -->
<!--                  ) %>% -->
<!--   plotly::layout(yaxis = list(title = "Recovery Rate", ticksuffix = "%"), -->
<!--                 xaxis = list(title = "Death Rate", ticksuffix = "%",  -->
<!--                              dtick = 1,  -->
<!--                              tick0 = 0), -->
<!--                 hovermode = "compare") -->

<!-- ```    -->

<!-- ### Cases Status Update for `r  max(coronavirus$date)` -->

<!-- ```{r} -->
<!-- daily_summary <- coronavirus %>%  -->
<!--   dplyr::filter(date == max(date)) %>% -->
<!--   dplyr::group_by(Country.Region, type) %>% -->
<!--   dplyr::summarise(total = sum(cases)) %>% -->
<!--   tidyr::pivot_wider(names_from = type, values_from = total) %>% -->
<!--   dplyr::arrange(-confirmed) %>% -->
<!--   dplyr::select(country = Country.Region, confirmed, recovered, death) -->


<!--   DT::datatable(data = daily_summary, -->
<!--                 rownames = FALSE, -->
<!--                 colnames = c("Country", "Confirmed", "Recovered", "Death"), -->
<!--                 options = list(pageLength = nrow(daily_summary), dom = 'tip')) -->
<!-- ``` -->

<!-- Data -->
<!-- ======================================================================= -->

<!-- ```{r} -->
<!-- coronavirus %>%  -->
<!--   dplyr::select(Date = date, Province = Province.State, Country = Country.Region, `Case Type` = type, `Number of Cases` = cases) %>% -->
<!--   DT::datatable(rownames = FALSE, -->
<!--             options = list(searchHighlight = TRUE,  -->
<!--                            pageLength = 20), filter = 'top') -->
<!-- ``` -->



About
=======================================================================

**The Coronavirus Dashboard**

This Coronavirus dashboard provides an overview of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic. This dashboard is built with R using the Rmakrdown framework and can easily reproduce by others. The code behind the dashboard available [here](https://github.com/RamiKrispin/coronavirus_dashboard)

**Data**

The input data for this dashboard is the [coronavirus](https://github.com/RamiKrispin/coronavirus) R package (dev version). The data and dashboard is refreshed on a daily bases. The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus [repository](https://github.com/RamiKrispin/coronavirus-csv)




**Packages**

* Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package.
* Visualization - the [plotly](https://plot.ly/r/) package for the plots and [leaflet](https://rstudio.github.io/leaflet/) for the map
* Data manipulation - [dplyr](https://dplyr.tidyverse.org/), and [tidyr](https://tidyr.tidyverse.org/)
* Tables - the [DT](https://rstudio.github.io/DT/) package

**Deployment and reproducibly**

The dashboard was deployed to Github docs. If you wish to deploy and/or modify the dashboard on your Github account, you can apply the following steps:

* Fork the dashboard [repository](https://github.com/RamiKrispin/coronavirus_dashboard), or
* Clone it and push it to your Github package
* Here some general guidance about deployment of flexdashboard on Github page - [link](https://github.com/pbatey/flexdashboard-example)

For any question or feedback, you can either open an [issue](https://github.com/RamiKrispin/coronavirus_dashboard/issues) or contact me on [Twitter](https://twitter.com/Rami_Krispin).

**Contribution**

The **Map** tab was contributed by [Art Steinmetz](@adababbage) on this [pull request](https://github.com/RamiKrispin/coronavirus_dashboard/pull/1). Thanks Art!

